Matroids from families of null hypotheses

### 2013-08-15 presentation/presentation.tex
added a couple of graph files, set up the pictures for qva example
fixed typo in hierarchical theorem

\begin{block}{Theorem}
  Assume that $M(\mathscr{H})$ neither contains loops nor
  parallels. Assume that hypotheses $H_1$ through $H_r$ have been
  rejected. Consider that hypotheses $H_{r+1}$ through $H_{r+t}$ are to
  be tested using at level $\alpha_r$ according to a prefixed order.
  If for some $1 \leq s \leq t$ holds
  \begin{equation}
    \label{eq:cond.hierarchical}
    \forall 1 \leq l < k \leq s: \; \exists i \leq r: i \sim \{l,k\},
  \end{equation}
  hypotheses $H_{r+1}$ through $H_{r+s}$ can be tested simultaneously
  at full level $\alpha_ra$.
\end{block}

@@

>>>>

\begin{block}{Theorem}
  Assume that $M(\mathscr{H})$ neither contains loops nor
  parallels. Assume that hypotheses $H_1$ through $H_r$ have been
  rejected. Consider that hypotheses $H_{r+1}$ through $H_{r+t}$ are
  to be tested at level $\alpha_r$ according to a prefixed order.  If
  for some $1 \leq s \leq t$ holds
  \begin{equation}
    \label{eq:cond.hierarchical}
    \forall 1 \leq l < k \leq s: \; \exists i \leq r: i \sim \{(r+l),(r+k)\},
  \end{equation}
  hypotheses $H_{r+1}$ through $H_{r+s}$ can be tested simultaneously
  at full level $\alpha_ra$.
\end{block}

@@

\begin{frame}
  \frametitle{General weighting strategies}
  \framesubtitle{QVA Example}

  \end{minipage} &
  \begin{minipage}{.6\textwidth}
    \begin{tikzpicture}[remember picture,overlay]
      \node[yshift=-50bp,xshift=-180bp] at (current page.north east){\input{qvameans}};
  \end{tikzpicture}
  \end{minipage}
\end{tabular}
\end{frame}
